```{r, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, cache = FALSE}

opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, comment = NA, 
  results = "asis", cache = FALSE)

source("header.R")
```

```{r}

opts <- list(
  title = "Mackenzie Wood Bison Population Dynamics Analysis 2015",
  author = "Thorley, J.L. and Boulanger, J."
)

rename = c(
  "bison" = "Population Dynamic",
  "env" = "Environmental",
  "PDO" = "Pacific Decadal Oscillation",
  "WSI" = "Winter Severity Index",
  "Rainfall" = "Rainfall",
  "SummerTemp" = "Summer Air Temperature", 
  "calf_cow" = "",
  "yearling_cow" = "",
  "herd" = "",
  "scalf" = "")
drop = NULL
```

```{r}
report_header(opts)
```

## Background

The Mackenzie Wood Bison (*Bison bison athabascae*) herd abundance has been 
estimated in four years since 1999 while herd composition data has been 
collected in all but three years. The herd composition data is collected in 
July while the abundance estimates are for March.

The primary questions this analysis attempts to answer are:

> What is the survival of calves, yearlings and adult in the Mackenzie herd?

> Is survival of calves in the Mackenzie herd driven by climatic conditions?

## Methods

### Data Preparation

The data were provided by Integrated Ecological Research.

In 2013 the herd experienced high mortality due to an anthrax outbreak. 
Consequently, the 2013 and 2014 data were excluded.

### Statistical Analysis

Hierarchical Bayesian models were fitted to the data using 
`r substr(R.version.string,1,15)` [@r_core_team_r:_2013] 
and JAGS 3.4.0 [@plummer_jags_2012]
which interfaced with each other via 
jaggernaut `r packageVersion("jaggernaut")` [@thorley_jaggernaut:_2013]. 
For additional information on hierarchical Bayesian modelling in the BUGS language, of which JAGS uses a dialect, the reader is referred to @kery_bayesian_2011 [pp. 41-44].

Unless specified, the models assumed vague (low information) prior distributions 
[@kery_bayesian_2011, pp. 36]. The posterior distributions were estimated from a minimum of 1,000 Markov Chain Monte Carlo (MCMC) samples thinned 
from the second halves of three chains [@kery_bayesian_2011, pp. 38-40]. 
Model convergence was confirmed by ensuring that Rhat [@kery_bayesian_2011, pp. 40]
 was less than 1.1 for each of the parameters in the model 
 [@kery_bayesian_2011, pp. 61]. 
Model adequacy was confirmed by examination of residual plots.

The posterior distributions of the *fixed* 
[@kery_bayesian_2011, pp. 75] parameters
are summarised in terms of a *point* estimate (mean), 
*lower* and *upper* `r opts_jagr("level") * 100`% credible limits (`r (1 - opts_jagr("level")) / 2 * 100`th 
and `r (1 - (1 - opts_jagr("level")) / 2) * 100`th percentiles), the standard deviation (*SD*), percent relative *error* (half the 95% credible interval as a percent of the point estimate) and *significance* [@kery_bayesian_2011, pp. 37, 42].

Variable selection was achieved by dropping *insignificant* 
[@kery_bayesian_2011, pp. 37, 42] fixed [@kery_bayesian_2011, pp. 77-82] variables
and *uninformative* random  variables.
A fixed variables was considered to be
insignificant if its significance was $\geq$ 0.05 while a random variable was
considered to be uninformative if its percent relative error was $\geq$ 80%.

The results are displayed 
graphically by plotting the modeled relationships between particular 
variables and the response with `r opts_jagr("level") * 100`% 
credible intervals (CRIs) with the 
remaining variables held constant. In general, 
continuous and discrete fixed variables are held constant at their mean and 
first level values respectively while random variables are held constant at their 
typical values (expected values of the underlying hyperdistributions) 
[@kery_bayesian_2011, pp. 77-82]. 
Where informative the influence of particular variables is expressed in terms 
of the *effect size* (i.e., percent change in the response variable) with 
`r opts_jagr("level") * 100`% CRIs 
[@bradford_using_2005].

### Model Description

The following model description observes several [conventions](http://www.poissonconsulting.ca/modeling/model-description-conventions.html).

The survival between life stages was estimated using a hierarchical Bayesian 
population dynamic state-space model [@kery_bayesian_2011].
Key assumptions of the population dynamic model include:

- A 50:50 sex ratio.
- Constant probability of a female adult calfing.
- Annually varying calf survival.
- Calf survival is able to vary with the Pacific Decadal Oscillation Index.
- Constant and identical yearling and adult survival.
- Clustering of cows with and without calves.
- Each year runs from May 15 to May 15.
- Survival does not vary seasonally.

In addition the effect of various environmental variables on calf
survival was tested by adding a standardised covariate to the population dynamic model.

```{r}
report_models(rename = rename, drop = drop)
```

## Results

```{r}
report_parameters(rename = rename, drop = drop)
  
report_figures(rename = rename, drop = drop)
```

## Acknowledgements

The organisations and individuals whose contributions have made this analysis report possible include:

- Poisson Consulting
    - Robyn Irvine

## References
